|

### 2023-03-14 paper_comparison/appendix.Rmd
update exp setup
init the Acknowledgement

@@

### Demographics

### Data collection interface

The survey data is collected via a self-hosted website designed by us. Once the participant is recruited from Prolific (ref here), it will be redirected to the entry page of our study website. An image of the entry page is provided in Figure \ref{fig:entry-page}. Then, the participant needs to submit the online consent form and fill in the demographic information as shown in \ref{fig:consent_form} and \ref{fig:metadata} respectively. Before evaluating lineups, participant also need to read the training page as provide in Figure \ref{fig:training-page} to understand the process. An example of the lineup page is given in Figure \ref{fig:lineup-page}. A half of the page is taken by the lineup image to attract participant's attention. The button to skip the selections for the current lineup is intentionally put in the corner of the bounding box with smaller font size, such that participants will not misuse this functionality.

## Batch effect size

@@

>>>>

### Data collection process

The survey data is collected via a self-hosted website designed by us.

(desc of the tech layers)

Once the participant is recruited from Prolific (ref here), it will be redirected to the entry page of our study website. An image of the entry page is provided in Figure \ref{fig:entry-page}. Then, the participant needs to submit the online consent form and fill in the demographic information as shown in \ref{fig:consent_form} and \ref{fig:metadata} respectively. Before evaluating lineups, participant also need to read the training page as provide in Figure \ref{fig:training-page} to understand the process. An example of the lineup page is given in Figure \ref{fig:lineup-page}. A half of the page is taken by the lineup image to attract participant's attention. The button to skip the selections for the current lineup is intentionally put in the corner of the bounding box with smaller font size, such that participants will not misuse this functionality.

```{r tech, out.width = "100%", fig.cap = "Diagram of online experiment setup. The server-side of the study website uses Flask as backend hosted on PythonAnywhere. And the client-side uses jsPsych to run experiment."}
knitr::include_graphics("img/experiment_tech.pdf")
```

## Demographics

@@

## Batch effect

@@

1. put #eval in appendix
3. compute the power of RESET test with different orders (considering dof) (focus on simple pattern possibly?)

### 2023-03-14 paper_comparison/paper_comparison/paper_comparison.Rmd
init the Acknowledgement

---
title: |
  A plot is worth a thousand tests: assessing residual diagnostics with visual inference
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
  - name: Susan VanderPlas
    affil: b
    email: susan.vanderplas@unl.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  data visualization; visual inference; hypothesis testing; residual plots;
header-includes: |
  \usepackage{lscape}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{xcolor}
  \definecolor{orange-red}{rgb}{1.0, 0.27, 0.0}
  \newcommand{\svp}[1]{{\textcolor{orange-red}{#1}}}
  \newcommand*{\Perm}[2]{{}^{#1}\!P_{#2}}%
output: rticles::tf_article
editor_options: 
  chunk_output_type: console
---

@@

1. software tools
2. point to github repo (create a new one)
3. summarise the supplementary material

@@

1. put #eval in appendix
2. examine batch effect in appendix
3. compute the power of RESET test with different orders (considering dof) (focus on simple pattern possibly?)

>>>>

---
title: |
  A plot is worth a thousand tests: assessing residual diagnostics with visual inference
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
  - name: Susan VanderPlas
    affil: b
    email: susan.vanderplas@unl.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  data visualization; visual inference; hypothesis testing; residual plots;
header-includes: |
  \usepackage{lscape}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
editor_options: 
  chunk_output_type: console
---

@@

The article was created with rticles (ref here), knitr (ref here) and R Markdown (ref here). The project's Github repository (link here) contains all materials required to reproduce this article.

# Supplementary material

The supplementary material is available at (link here). It includes more details about the experimental setup, the derivation of the effect size, the effect of data collection period, and the estimate of  $\alpha$.

@@
